Test-driven Knowledge Graph Construction

### 2023-05-08 doc/paper4.tex
Reduce 'based on'

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  We propose how to construct knowledge graphs using a method based on user requirements formulated as competency questions. It suggests to formalize the competency questions as SPARQL queries wrapped as SHACL constraints allowing them to be used as automated tests. The method defines a process to guide knowledge graph construction based on feedback from tests. It aims to reduce the engineering effort required to construct a knowledge graph that meets the requirements, while assessing the quality of semantic artifacts produced in this effort. We intend the method to provide a solid engineering basis for knowledge graph construction using the lessons learnt from software development and based on open standards. We demonstrate using the method to construct a knowledge graph about antigen covid tests and reflect on the proposed method.
\end{abstract}

@@

We propose how to construct knowledge graphs using a standards-based method founded upon user requirements formulated as competency questions (CQs). It suggests to formalize the CQs as SPARQL queries \cite{SPARQL2013} and wrap them as SHACL constraints \cite{SHACL2017} in order to allow them to be executed as automated tests. The method defines a process guiding knowledge graph construction based on feedback from tests. It aims to reduce the effort required to construct a knowledge graph that meets its requirements and passes quality assessment of semantic artifacts, such as ontologies, that are made in the process.

@@

Some errors were not detected by the tests based on CQs. For example, when querying the knowledge graph, we found that the data transformation to RDF mistakenly created IRIs of manufacturers based on their antigen covid test identifiers. Consequently, the resulting data related each manufacturer to one antigen covid test, so that it was not possible to group multiple tests by the same manufacturer. A common response to finding errors not covered by tests is improving test coverage to enable detecting the errors found and avoid future regressions. We followed this practice and added a CQ comparing a given manufacturer's antigen covid tests. The CQ presupposed that there are manufacturers offering more than one test and would therefore fail in case of the above-described error. Apart from fixing the way we generated manufacturers' IRIs, we spent further effort on de-duplicating manufacturers via post-processing by SPARQL Update operations.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  We propose how to construct knowledge graphs using a method based on user requirements formulated as competency questions. It suggests to formalize the competency questions as SPARQL queries wrapped as SHACL constraints allowing them to be used as automated tests. The method defines a process to guide knowledge graph construction by feedback from tests. It aims to reduce the engineering effort required to construct a knowledge graph that meets the requirements, while assessing the quality of semantic artifacts produced in this effort. We intend the method to provide a solid engineering basis for knowledge graph construction that uses the lessons learnt from software development and is built on open standards. We demonstrate using the method to construct a knowledge graph about antigen covid tests and reflect on the proposed method.
\end{abstract}

@@

We propose how to construct knowledge graphs using a standards-based method founded upon user requirements formulated as competency questions (CQs). It suggests to formalize the CQs as SPARQL queries \cite{SPARQL2013} and wrap them as SHACL constraints \cite{SHACL2017} in order to allow them to be executed as automated tests. The method defines a process guiding knowledge graph construction that is based on feedback from tests. It aims to reduce the effort required to construct a knowledge graph that meets its requirements and passes quality assessment of semantic artifacts, such as ontologies, that are made in the process.

@@

Some errors were not detected by the tests implementing the CQs. For example, when querying the knowledge graph, we found that the data transformation to RDF mistakenly created IRIs of manufacturers based on their antigen covid test identifiers. Consequently, the resulting data related each manufacturer to one antigen covid test, so that it was not possible to group multiple tests by the same manufacturer. A common response to finding errors not covered by tests is improving test coverage to enable detecting the errors found and avoid future regressions. We followed this practice and added a CQ comparing a given manufacturer's antigen covid tests. The CQ presupposed that there are manufacturers offering more than one test and would therefore fail in case of the above-described error. Apart from fixing the way we generated manufacturers' IRIs, we spent further effort on de-duplicating manufacturers via post-processing by SPARQL Update operations.
